Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-13 prop_letter.tex
Revert "prop_letter.tex Some formating updates. For example, remove extra"
This reverts commit e743a017237cf096dcd652930c2be3ce40598d7c.

# Conflicts:
#	prop_letter.tex

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality \cite{Peres2003,BarrettKent2004}.  For example,
Meyer \cite{PhysRevLett.83.3751} and Mermin \cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem \cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.

Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems \cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures \cite{JamisonLodwick2004} to the quantum domain.  We begin by
axiomatizing a quantum interval-valued probability measure (QIVPM)
framework exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability
measures \cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
One result is that the expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude
that they correspond to the limit of an infinite number of precise
intervals, and the set of crypto-deterministic intervals (the set
$\{\imposs,\necess\}$), respectively.

@@

% Textbook quantum mechanics asserts that the probability of a
% measurement can be computed from wave function of the system and the
% measuring observable \emph{exactly} while real measurements must be
% finite precision.  Whether finite precision measurement in reality
% affect the idealized quantum concept, e.g.,
% contextuality \cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
% and the very foundation of quantum mechanics is still a problem. In
% this letter, we model the finite precision quantum measurement by
% quantum interval-valued probability measures (IVPMs) which provides
% not only a uniform framework to understand Gleason's
% theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
% Kochen-Specker
% theorem \cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
% but also some examples which cannot be explained by the Born
% rule \cite{Born1983,peres1995quantum,544199,Jaeger2007}.

% The tension between finite precision measurement and the foundation of
% quantum mechanics sharpened, when the original definition of
% contextuality based on infinitely precise numbers is proved not
% experimental verifiable \cite{PhysRevLett.83.3751,Kent1999}.  After a
% long debate \cite{Mermin1999,Peres2003,BarrettKent2004}, people are
% still trying to update the definition of contextuality when they want
% to perform further
% experiments \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

% We found that finite precision measurement affects not only
% contextuality but also the fundamental rule computing probability from
% a state.  In the early formulation of quantum mechanics, von Neumann
% essentially formulated a quantum state as a density matrix while
% Mackey formulated a quantum state as a quantum probability measure
% which are proved by Gleason to be the essentially same as a density
% matrix \cite{Varadarajan2008}.  Combining quantum probability measures
% and the classical IVPM \cite{JamisonLodwick2004} which could be used
% to formulate classical finite precision measurement, we can define
% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
% compatible with any density matrix according to the Born rule. Similar
% to revising the definition of contextuality because of finite
% precision measurement, the very basic definition of a quantum state or
% how to compute the probability from a state might need to be refined
% when we consider the finite precision measurement. This can also
% provide a new quantum phenomena different from the classical world,
% because IVPMs become classical so that the non-Born IVPMs disappears
% when we restricting the domain of quantum IVPMs on a commuting
% sub-event space.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events \cite{Kolmogorov1950}.  In the quantum case, the
events of interest are the \emph{projection operators} $P$. This set
includes the empty projection $\mathbb{0}$, the identity
projection $\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a
well-defined quantum probability
space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_i$ is associated with a probability $\mu(P_i)$ subject
to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$, we
have:
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}

@@

% In conventional quantum theory (CQT), when we measure a property
% $\mathbf{O}$ of a physical system whose state is represented by a
% density matrix $\rho$, the probability to obtain the value $\lambda$
% of that property is determined by the Born rule
% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
% Hermitian operator
% $\mathbf{O}$ \cite{Born1983,peres1995quantum,544199,Jaeger2007}.
% Alternatively, one may say that the state $\rho$ determines the
% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
% from the set $\events$ of all possible projectors $P$ onto the
% interval $[0,1]$, and satisfies the following probability axioms 
% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:

% \begin{itemize}
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_iP_j=\delta_{ij}P_i$,
% we have 
% \begin{equation}
% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
% \textrm{ .}\label{eq:QuantumProbability-Addition}
% \end{equation}
% \end{itemize}
% Conversely, given any quantum probability measure $\mu:\events\rightarrow[0,1]$
% satisfying the above axioms, Gleason's theorem asserts that there
% exists a unique state $\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
% in a Hilbert space of dimension $d\geq3$ \cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

% Furthermore, if we express an observable $\mathbf{O}$ as its spectrum
% decomposition $\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
% value of $\mathbf{O}$ is given by \cite{peres1995quantum,544199,Jaeger2007}
% \begin{equation}
% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
% \end{equation}

% To formalize the idea of finite precision measurement, we next
% introduce the notion of quantum interval-valued probability measures
% (\emph{IVPMs}) $\bar{\mu}$. The latter replaces the infinitely precise
% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
% arithmetic operations on intervals
% satisfy \begin{subequations}\label{eq:interval-operations}
% \begin{eqnarray}
%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
%  &  & x[l,r]=\begin{cases}
% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
% [xr,xl] & \textrm{for }x\le0\textrm{ .}
% \end{cases}
% \end{eqnarray}
% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
% defined by the axioms: 
% \begin{itemize}
% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
% \begin{equation}
% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
% \end{equation}
% \end{itemize}
% condition that provides only a bound and not an equivalence as in
% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
% \[
% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
% \]

@@

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum IVPM, i.e., given observations done with finite
resources. Since the probabilities are now intervals, it is intuitive
to say a state $\rho$ is consistent with $\bar{\mu}$ on a projector $P$
if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$.

Since our measurement is fuzzy, generally there are more than one
state consistent with a particular quantum IVPM. For example, consider
three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called $\imposs$ and
$\necess$ as before, and \emph{$\left[0,1\right]$} is called $\unknown$ because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question,
and any state is consistent with $\bar{\mu}_{1}$ on any projectors.

@@

Quantum IVPMs become classical IVPMs \cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM $\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices $\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state $p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability $p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

@@

\begin{definition}
$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$ \cite{Griffiths2003}.
\end{definition}

Based on Shapley's classical result \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
we have the following theorem.

\begin{thm}\label{thm:Shapley}For every convex quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$,
if a sub-event space $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@

Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express an observable as
its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral \cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

@@

\begin{definition}Given an observable $\mathbf{O}$ with its spectrum
decomposition (\ref{eq:spectrum-decomposition}). A set of projectors $\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal sub-event space containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$.\end{definition}

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.

Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable byextending classical interval-valued probability
measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
axiomatizing a quantum interval-valued probability measure (QIVPM)
framework exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability
measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
One result is that the expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude
that they correspond to the limit of an infinite number of precise
intervals, and the set of crypto-deterministic intervals (the set
$\{\imposs,\necess\}$), respectively.

@@

% Textbook quantum mechanics asserts that the probability of a
% measurement can be computed from wave function of the system and the
% measuring observable \emph{exactly} while real measurements must be
% finite precision.  Whether finite precision measurement in reality
% affect the idealized quantum concept, e.g.,
% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
% and the very foundation of quantum mechanics is still a problem. In
% this letter, we model the finite precision quantum measurement by
% quantum interval-valued probability measures (IVPMs) which provides
% not only a uniform framework to understand Gleason's
% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
% Kochen-Specker
% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
% but also some examples which cannot be explained by the Born
% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

% The tension between finite precision measurement and the foundation of
% quantum mechanics sharpened, when the original definition of
% contextuality based on infinitely precise numbers is proved not
% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
% still trying to update the definition of contextuality when they want
% to perform further
% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

% We found that finite precision measurement affects not only
% contextuality but also the fundamental rule computing probability from
% a state.  In the early formulation of quantum mechanics, von Neumann
% essentially formulated a quantum state as a density matrix while
% Mackey formulated a quantum state as a quantum probability measure
% which are proved by Gleason to be the essentially same as a density
% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
% to formulate classical finite precision measurement, we can define
% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
% compatible with any density matrix according to the Born rule. Similar
% to revising the definition of contextuality because of finite
% precision measurement, the very basic definition of a quantum state or
% how to compute the probability from a state might need to be refined
% when we consider the finite precision measurement. This can also
% provide a new quantum phenomena different from the classical world,
% because IVPMs become classical so that the non-Born IVPMs disappears
% when we restricting the domain of quantum IVPMs on a commuting
% sub-event space.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
events of interest are the \emph{projection operators} $P$. This set
includes the empty projection~$\mathbb{0}$, the identity
projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a
well-defined quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_i$ is associated with a probability $\mu(P_i)$ subject
to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$, we
have:
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}

@@

% In conventional quantum theory (CQT), when we measure a property
% $\mathbf{O}$ of a physical system whose state is represented by a
% density matrix~$\rho$, the probability to obtain the value $\lambda$
% of that property is determined by the Born rule
% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
% Hermitian operator
% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
% Alternatively, one may say that the state $\rho$ determines the
% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
% from the set $\events$ of all possible projectors $P$ onto the
% interval $[0,1]$, and satisfies the following probability axioms~
% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:

% \begin{itemize}
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_iP_j=\delta_{ij}P_i$,
% we have 
% \begin{equation}
% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
% \textrm{ .}\label{eq:QuantumProbability-Addition}
% \end{equation}
% \end{itemize}
% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
% satisfying the above axioms, Gleason's theorem asserts that there
% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
% \begin{equation}
% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
% \end{equation}

% To formalize the idea of finite precision measurement, we next
% introduce the notion of quantum interval-valued probability measures
% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
% arithmetic operations on intervals
% satisfy \begin{subequations}\label{eq:interval-operations}
% \begin{eqnarray}
%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
%  &  & x[l,r]=\begin{cases}
% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
% [xr,xl] & \textrm{for }x\le0\textrm{ .}
% \end{cases}
% \end{eqnarray}
% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
% defined by the axioms: 
% \begin{itemize}
% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
% \begin{equation}
% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
% \end{equation}
% \end{itemize}
% condition that provides only a bound and not an equivalence as in
% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
% \[
% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
% \]

@@

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum IVPM, i.e., given observations done with finite
resources. Since the probabilities are now intervals, it is intuitive
to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$.

Since our measurement is fuzzy, generally there are more than one
state consistent with a particular quantum IVPM. For example, consider
three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question,
and any state is consistent with $\bar{\mu}_{1}$ on any projectors.

@@

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} whenthe space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

@@

\begin{definition}
$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{definition}

Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
we have the following theorem.

\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@

Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express an observable as
its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal sub-event space containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$.\end{definition}
